---
title: "HW5_Tolon"
author: "Abbie Tolon"
date: "February 19, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##0. Conduct any data import and library steps needed to complete this homework using below code.

```{r }
#rm(list = ls()) #clear global environment

library(dplyr)
library(ggplot2)
library(odds.n.ends)
library(car)

BRFSS<-read.csv(
"https://raw.githubusercontent.com/kijohnson/ADA_Spring_2019/master/BRFSS2017_10percent_v2.csv", 
header=TRUE, sep=",", na.strings=FALSE)

#code to drop X column, which is not needed
col.dont.want<-"X"
BRFSS<-BRFSS[,!names(BRFSS)%in%col.dont.want, drop=F]
print(head(BRFSS))
```

## Look at each variable used in the analysis to get a handle on class, observation numbers, missing data etc.

```{r}
#check class of variables
class(BRFSS$bmi) #is factor
class(BRFSS$seatbelt)#some missing/refused data (is factor)
class(BRFSS$sex) #is factor
class(BRFSS$X_AGE80) #is integer

#use table function to look at categorical variable numbers
table(BRFSS$seatbelt)#some missing/refused data
table(BRFSS$sex)#some refused data

#use summary function to look at continuous variables
summary(BRFSS$X_AGE80)#no missing data
BRFSS$bmi<-as.numeric(as.character(BRFSS$bmi))
summary(BRFSS$bmi)#no missing data
```

##1. The first steps you take in this analysis are: a. You make a new seatbelt variable categorizing seatbelt use as 'Always' vs. 'Not always' with 'Always' being coded as 1 and 'Not always' being coded as 0 (include 'Never', 'Sometimes', and 'Nearly always' in your 'Not always' category). b. You cross-check how many observations are in the new binary seatbelt category with the original variable to make sure that the number is correct.

a) Make the new dichotomous seatbelt variable

```{r}
#First, viewing unique values because it's difficult for me to tell what all the value names are via the console
View(unique(BRFSS$seatbelt))

#First changing seatbelt to a character variable, so that the recoding works properly
BRFSS$seatbelt <- as.character(BRFSS$seatbelt)

#Check the class
class(BRFSS$seatbelt) #is character 

#Next, recode the seatbelt variable into "Always" and "Not Always"

#Always=1
BRFSS$seatbelt_binary[
  BRFSS$seatbelt=="Always"]<-1 #Assign 1 to those who responded "Always" to the seatbelt question

#Not Always=0
BRFSS$seatbelt_binary[
  BRFSS$seatbelt=="Never"|BRFSS$seatbelt=="Sometimes"|BRFSS$seatbelt=="Nearly always"|BRFSS$seatbelt=="Seldom"]<-0 #Assign 0 to those who responded "Never", "Sometimes", "Nearly always", or "Seldom" to the seatbelt question. 

#Leaving out the following values from the recode: 
#"Refused", "NA", "Never drive or ride in a car", and "Don't know/Not sure"

#Make this a factor variable and add applicable labels 
BRFSS$seatbelt_binary<-factor(BRFSS$seatbelt_binary, levels=c(0,1), labels=c("Not Always", "Always"))
```

b) Cross-check to see how many observations are in the new binary category 

```{r}
#check to make sure re-classification worked
table(BRFSS$seatbelt, BRFSS$seatbelt_binary) #the recoding looks good!
```

##2. An important first step in any regression modeling exercise is to know your data. One of the components of knowing your data includes data visualization. You decide to make a box plot to visually examine how the distribution of bmi varies by the binary seatbelt use variable.

For comparing regression models, it is important to have the same number of observations. For this analysis we will do a complete case analysis. The below code creates an analytic dataset and removes any observations with missing/refused values for variables to be used in data analysis.

```{r}
#Complete case analysis exclusions of missing/refused data
myvars<-c("rowID", "X_AGE80", "age_cat", "sex", "bmi", "seatbelt_binary")
BRFSS_ex<-BRFSS[myvars]
BRFSS_ex<-na.omit(BRFSS_ex)
BRFSS_ex<-BRFSS_ex[which(BRFSS_ex$sex!="Refused"),]
BRFSS_ex<-BRFSS_ex[which(BRFSS_ex$age_cat!="Don't know/refused/missing"),]
```

Now that we have complete cases, we can visualize the data with box plots

```{r}
#Make a box plot to visually examine how the distribution of bmi varies by the binary seatbelt use variable 

#First, check the class 
class(BRFSS_ex$seatbelt_binary) #Is numeric 
BRFSS_ex$seatbelt_binary<- as.factor(BRFSS_ex$seatbelt_binary) #changing to factor 

#plot the boxplots with seatbelt and bmi
BRFSS_ex %>% 
  ggplot(aes(x = seatbelt_binary, y = bmi)) +
  geom_boxplot(aes(fill = seatbelt_binary)) +
  labs(x = "Wears a Seatbelt (Not Always vs. Always)", y = "BMI (kg/m2)") +
  theme_bw() +
   theme(plot.title = element_text(hjust = 0.5), 
        legend.background = element_rect(color = "black", 
                                         fill = "gray")) 
```

##3. You check whether running age and bmi as continous variables is appropriate for your regression models. You describe whether it is appropriate or not for each variable.

Completing the test for BMI first

```{r}
#Use Box Tidwell approach
linearTermBMI <- BRFSS_ex$bmi * log(BRFSS_ex$bmi) #creating the term to test for linearity 

#Testing assumption of linearity using the box tidwell technique 
BoxTidBMI <- glm(seatbelt_binary ~ bmi + linearTermBMI, data = BRFSS_ex, family = "binomial")

#View results
summary(BoxTidBMI)

#The coefficient for the interaction term we created is NOT significant.
#Therefore, it IS appropriate to use BMI in our model 
```
Completing the same procedure now, for age

```{r}
#Use Box Tidwell approach
linearTermAge <- BRFSS_ex$X_AGE80 * log(BRFSS_ex$X_AGE80) #creating the term to test for linearity 

#Testing assumption of linearity using the box tidwell technique 
BoxTidAge <- glm(seatbelt_binary ~ X_AGE80 + linearTermAge, data = BRFSS_ex, family = "binomial")

#View results
summary(BoxTidAge)

#The coefficient for the interaction term we created is NOT significant. 
#Therefore, it IS appropriate to use Age in our model 
```

##4. You make the decision based on these results to first run a univariate logistic regression model for bmi and calculate ORs and 95% CIs.

```{r}
#seatbelt univariate logistic model with bmi as the variable
bmiLogit <- glm(seatbelt_binary ~ bmi, data=BRFSS_ex, family="binomial")
  summary(bmiLogit)
  
#calculate and print ORs and 95% CIs  
  ORbmi<-exp(cbind(OR = coef(bmiLogit), confint(bmiLogit))) #calculate ORs and 95% CIs
  ORbmi #print ORs and 95% CIs
```

##5. You then decide to run a multivariate logistic regression model that includes bmi plus age_cat and sex in the model as covariates.

```{r}
#Multivariate logistic model for age, bmi, and sex
bmiagesexLogit <- glm(seatbelt_binary ~ as.factor(age_cat) + bmi + as.factor(sex), data=BRFSS_ex, family="binomial")
  summary(bmiagesexLogit)
#Note to self: Female is reference; Age 18-24 is reference
  
#calculate and print ORs and 95% CIs  
ORmodel<-exp(cbind(OR = coef(bmiagesexLogit), confint(bmiagesexLogit))) #calculate ORs and 95% CIs
  ORmodel #print ORs and 95% CIs
```

##6. Next, you look for influential observations and determine the top 5 influential observations using a Cook's Distance plot.

```{r}
#Cook's D plot
plot(bmiagesexLogit, which=4, id.n=5, col="red", cex.id=0.6) 

#The top 5 influental observations are #674, #8238, #11076, #13764, #42346
```

##7. Based on these findings, you exclude the top 5 influential observations and compare Betas for bmi between models with and without these observations.

```{r}
#dropping the top 5 influential observations (674, 8238, 11076, 13764, 42346)
bmiagesexLogit.modex <- update(bmiagesexLogit,subset=c(-674, -8238, -11076, -13764, -42346))

#compare coefficients between models with and without influential observations
compareCoefs(bmiagesexLogit, bmiagesexLogit.modex) 
```

##8. Next, you decide to evaluate model classification performance. First, you run the below code to generate a balanced sample to improve model performance since unbalanced models will give poor sensitivity or specificity

Running below code to generate balanced sample and improve model performance

```{r}
#create new dataset with diabetes_binary= 0
#table(BRFSS_ex$seatbelt_binary)
set.seed(1)
BRFSS_one<-sample_n(BRFSS_ex[which(BRFSS_ex$seatbelt_binary=='Always'),], size=4265) # sample from always seat belt wearers to make them 1:1 as not always seat belt wearers

BRFSS_zero<-BRFSS_ex[which(BRFSS_ex$seatbelt_binary=='Not Always'),] # Not always seatbelt wearers only

BRFSS_balance<- rbind(BRFSS_zero,BRFSS_one) #Combine these datasets by row 

table(BRFSS_balance$seatbelt_binary)
```

You then take the following steps to evaluate model performance. 

a. You run your model again with the new dataset you created. 

```{r}
#Multivariate logistic model for age, bmi, and sex with the new dataset (BRFSS_balance)
bmiagesexLogit2 <- glm(seatbelt_binary ~ bmi + age_cat + sex, data=BRFSS_balance, family="binomial")
  summary(bmiagesexLogit2)
#Note to self: Female is reference; Age 18-24 is reference
  
#calculate and print ORs and 95% CIs  
ORmodel<-exp(cbind(OR = coef(bmiagesexLogit2), confint(bmiagesexLogit2))) #calculate ORs and 95% CIs
  ORmodel #print ORs and 95% CIs
```

b. You determine the number of 'Always' seatbelt wearers vs. 'Not always' seatbelt wearers predicted by your model. 

c. From these numbers (and the actual data), you calculate and report the sensitivity and specificity of your model (hint: you can use the odds.n.ends function for both b and c). 

```{r}
#Use odds.n.ends function to calculate the sensitivity and specificity of the model and to view predicted vs. observed 
odds.n.ends(bmiagesexLogit2)

#There are 3637 total "Always" seatbelt wearers predicted, vs. 5373 "Not Always" seatbelt wearers predicted 

#The sensitivity of our model is 51.84% and the specificity of our model is 69.94%; the model correctly predicts a positive result (Always wears a seatbelt) 51.84% of the time, and correctly predicts a negative results (Not Always wears a seatbelt) 69.94% of the time. 
```

d. You then generate an ROC curve and report the AUC.

```{r}
#First plot/generate the ROC curve
preds<-predict(bmiagesexLogit2, newdata=BRFSS_balance, type='response') #get predicted probabilities from the model (bmiagesexLogit2) and the actual values for seatbelt from the BRFSS_balance dataset

ROCR=prediction(as.numeric(preds), as.numeric(BRFSS_balance$seatbelt_binary)) #predicted probs, values of dependent variable. *Note need as.numeric specification for below

perf=performance(ROCR,"tpr", "fpr") # tpr is what to plot on y axis and fpr is what to plot on x axis
plot(perf, colorsize=T, color="red", print.cutoffs.at=seq(0,1,0.1))
abline(a=0, b= 1)

#Next, obtain the threshold value from the curve with the highest sensitivity and specificity
ss <- performance(ROCR, "sens", "spec")
plot(ss)
ssval<-ss@alpha.values[[1]][which.max(ss@x.values[[1]]+ss@y.values[[1]])]
ssval

#Set threshold at 0.4855555 and get a confusion matrix
t=0.4855555
pred_class=ifelse(preds>t, 'Always','Not Always')
addmargins(table(pred_class=pred_class,observed=BRFSS_balance$seatbelt_binary))

#Now, get the AUC
auc.perf = performance(ROCR, measure = "auc")
auc.perf@y.values

#The AUC is only 0.643; this means it does not do a great job at predicting people who always wear a seatbelt. 
```
##9. Finally, you interpret the results from this analysis in one paragraph.

The above analysis was conducted to see whether there was a statistically significant logistic regression model that could predict the probability of whether a person "always" wears a seatbelt, based on their age, sex, and bmi. After cleaning the data and creating a balanced sample, various statistical analyses were completed. After running the full and final logistic model, it was determined that each variable statistically significantly predicted the probability of always wearing a seatbelt, meaning we reject the null hypotheses for our predictors. Additionally, sensitivity and specifity were calculated to see how well our model does at correctly predicting whether a person always or does not always wear a seatbelt. The analysis displayed that our model was more specific than sensitive. In other words, it did better at correctly predicting those who do not always wear a seatbelt (70%) than it did at correctly predicting those who always wear a seatbelt (52%). Finally, an ROC curve was generated in order to report the AUC. The AUC displayed that, while the model is technically statistically significant, it does not actually do a great job at predicting the probability that a person always wears a seatbelt. Therefore, researchers must proceed with caution when utilizing this model to make predictions on seatbelt use.
