---
title: "RShiny Workshop"
author: "Abbie Tolon"
date: "February 12, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Install the shiny package
Install the shinythemes package
Install the rsconnect package

```{r}
#install.packages("shiny")
#install.packages("shinythemes")
#install.packages("rsconnect")

library("shiny")
library("shinythemes")
library("rsconnect")
```

## Presentation 

R Shiny allows you to build web apps that can be hosted locally or publicly (used for entertainment, dashboards, data visualization, and sharing information)

The computer has to be actively running R while you're running the Shiny app

##Main Steps 
1. Write a program in R
2. Convert it to Shiny app
3. Make it pretty!
4. Host it somewhere to share 

```{r pressure, echo=FALSE}
#Template for creating the input (ui="user interface")
ui <- fluidPage(
  sliderInput(inputId = "num",
              label = "Choose a number",
              value = 25, min = 1, max = 100),
  plotOutput('scatplot') #name of the output object = scatplot; type of output=plot
) 
```

```{r}
server <- function(input, output){
  #randomly generate x and error
x=rnorm(200, mean=50, sd=20)
e=rnorm(200, mean=0, sd=300)

#render draws it in such a way that it's compatible with the ui. 
output$scatplot <- renderPlot({
beta <- input$num
y=10 + beta*x + e

#the regression function 
dat <- as.data.frame(x,y)

#Create scatter plot
ggplot(dat, aes(x,y)) + theme_bw() + geom_point(col="purple", size=2, alpha=.5)})}

shinyApp(ui=ui, server=server)
```

##Building the User Interface
Need an input and an output (refer to template in code chunk above)
Next, you build the server code

##Reactivity

Input objects have to be nested within a render function 

```{r}
#Secret code from shinyapps.io to be able to work on my computer 
rsconnect::setAccountInfo(name='abbie-rose', token='00BD5A2A399EDA1E30FFA9343E61F349', secret='6l498BjWi7qylVXAJ4i2mwu5N/OSUih0s/vLw9IP')
```

reactive() creates an object
reactiveValues() creates a list
observeEvent() triggers code to run on server 

##Make things pretty!
